\section*{Acknowledgments}
I am sincerely thankful to Dr. Erman Ayday and Dr. Youngjin Yoo for their mentorship and collaboration on the ShareTrace project and the various xLab endeavors. As a result of their generous support, I have learned about the challenges of distributed computing and the exciting prospects of applying decentralized and self-sovereign technologies to solve impactful problems. I believe that my experiences with Dr. Ayday and Dr. Yoo have significantly contributed to my first career opportunity at Amazon; and for that, I cannot thank them enough.

Research reported in this paper was partly supported by the National Science Foundation (NSF) under grant number NSF CCF 2200255 and Cisco Research University Funding grant number 2800379. This work made use of the High Performance Computing Resource in the Core Facility for Advanced Research Computing at Case Western Reserve University.

In reference to IEEE copyrighted material which is used with permission in this thesis, the IEEE does not endorse any of Case Western Reserve University’s products or services. Internal or personal use of this material is permitted. If interested in reprinting/republishing IEEE copyrighted material for advertising or promotional purposes or for creating new collective works for resale or redistribution, please go to \url{http://www.ieee.org/publications_standards/publications/rights/rights_link.html} to learn how to obtain a License from RightsLink. If applicable, University Microfilms and/or ProQuest Library, or the Archives of Canada may supply single copies of the thesis.
\clearpage